### 2011-05-11 paper.tex
Filled in polytime reductions

This follows from the following four lemmas:

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}
\end{proof}
We wish to show that if $f \in \Sigma \cdot C$, then $f \circ T \in \Sigma \cdot C$. We have that 
\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Pi \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\bp \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\parity \cdot C$ is closed under polynomial time reductions.
\end{lemma}
\begin{proof}

\end{proof}

>>>>

This follows from the following lemma:

\begin{lemma}
If $C$ is a complexity class closed under polynomial time reductions. Then $\Sigma \cdot C$, $\Pi\cdot C$, $\bp\cdot C$, and $\parity\cdot C$ are closed under polynomial time reductions.
\end{lemma}
\begin{proof}
We wish to show that if $f \in \op \cdot C$, then $f \circ T \in \op \cdot C$. We have a $g \in C$ such that $g(\langle T(x), y\rangle)$ has the correct relation to $f$ for $f$ to be in $\op \cdot C$ (for example, for $\Sigma$, if $f(T(x)) = 1$, then there is a $y$ with $g(\langle T(x), y\rangle) = 1$ and if $f(T(x)) = 0$, then for all $y$ $g(\langle T(x), y \rangle) = 0$). However, we can construct a polynomial time Turing machine that takes $\langle x, y\rangle$ to $\langle T(x), y\rangle$, so since $C$ is closed under polynomial time reductions, we have that $h(\langle x,y\rangle) = g(\langle T(x),y\rangle)$ is a function in $C$. As $h(\langle x,y\rangle)$ has the same relation to $f$ as $g$ does to $f \circ T$, we have that $f \in \op \cdot C$, as desired.
\end{proof}
